### 2015-03-10 Neutral_simulPow.Rmd
Update reviewer 1 specific comments #3-#5 add colorblind palette
Update reviewer 1 specific comments #7 #8

p1 <- plotPow_MeanSp_difR(comp_ADq10)
ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)

p2 <- plotPow_MeanSp_difR(comp_ADq10,512)
ggsave("powADq10_DifR_512.png", width=6,height=6,units="in",dpi=600)

@@

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
#g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
g

@@

# Plot Dq for simulations in txt files (NULL)
#

setwd("Simul")
plotNeutral_Dq(64,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog64_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(8,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog8_256.png", width=8,height=4,units="in",dpi=600)

setwd("Simul")
plotNeutral_Dq(256,256,500,"L",NULL) # Null use previous simulations 
setwd("..")
ggsave("Dq_NeuLog256_256.png", width=8,height=4,units="in",dpi=600)

>>>>

#p1 <- plotPow_MeanSp_difR(comp_ADq10)
#ggsave("powADq10_DifR_256.png", width=6,height=6,units="in",dpi=600)

p1 <- plotPow_MeanSp_RplR(comp_ADq10)
ggsave("powADq10_RplR_256.png", width=8,height=8,units="in",dpi=600)

p2 <- plotPow_MeanSp_RplR(comp_ADq10,512)
ggsave("powADq10_RplR_512.png", width=6,height=6,units="in",dpi=600)

@@

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
#g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))

@@

### 2015-03-10 SP_simul.Rmd
Update reviewer 1 specific comments #7 #8

@@

# Plot of the Regular and Randomized spatial pattern for a uniform & Logseries SAD with 64 species and side=256
#
g <- plotSAD_SpatPat(64,256,"B")
g

#g <- plotSAD_SpatPat(64,256,"U")
#g 
setwd("..")
ggsave("spat_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")

@@

zq <- readDq_fit(256,64,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))
g

setwd("Simul")
zq <- readDq_fit(256,8,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_8_256.png", width=8,height=6,units="in",dpi=600)

setwd("Simul")
zq <- readDq_fit(256,256,"Uniform")
g <- plotDqFitG(zq)
g
setwd(oldcd)
ggsave("DqFit_Unif_256_256.png", width=8,height=6,units="in",dpi=600)

>>>>

Here I generate figures 1 and 2 for the appendix

@@

# Plot of the Regular and Randomized spatial pattern for a uniform & Logseries SAD with 64 species and side=256
#
g <- plotSAD_SpatPat(64,256,"B")

setwd("..")
ggsave("spat_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")

@@

zq <- readDq_fit(256,64,"Uniform")

g <- plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))

setwd("Simul")
zq <- readDq_fit(256,8,"Uniform")
g <- plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_8_256.png", width=8,height=6,units="in",dpi=600)

setwd("Simul")
zq <- readDq_fit(256,256,"Uniform")
g <- plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_256_256.png", width=8,height=6,units="in",dpi=600)
